---
title: "Practical_Machine_Learning"
output: html_document
---

##Remove zero covariates and NA columns
First we identify and remove variables that will make inisgnicant or null contribution to the model.
We also select a training and testing set.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#setwd('C:/Users/jbarrera/Desktop/PML_WriteUp')
setwd("C:/Users/Jor/Dropbox/DSciencesCoursera/08_PracticalML/WriteupProject");
```

```{r,echo=TRUE, message=FALSE, warning=FALSE}
library(caret);
train_df <- read.csv("pml-training.csv", header=TRUE)
zero_var <- nearZeroVar(train_df)
train_df <- train_df[,-zero_var]
train_df <- train_df[,colSums(is.na(train_df))<1000]
inTrain <- createDataPartition(y=train_df$classe,p=0.6,list=FALSE)  # trainning is around 60% 
training <- train_df[inTrain,] 
testing <- train_df[-inTrain,]    

```
A total of 101 variables have been removed, for example: 
```{r,echo=FALSE, message=FALSE, warning=FALSE}
head(names(train_df)[zero_var])
```



##Cross Validation
For cross valudation I am using 10-Fold, hence I am using
```{r, echo=TRUE}
ctrl2 <- trainControl(method = "cv", number=10);
```

##Model Selection
About the moedel selection lm and glm are out of question as they are not intended for classification. I will consider classification with trees, random forest and boosting with trees.

###Classification with trees
```{r, echo=TRUE}
modfitdt <- train(classe~., method="rpart", data=training, trControl=ctrl2)
pred_dt <- predict(modfitdt,newdata=testing)
table(pred_dt,testing$classe)
```


###Random Forest
```{r, echo=TRUE,eval=FALSE}
modfit_rf <- train(classe~., method="rf", data=training, trControl=ctrl2)
pred_rf <- predict(modfit_rf,newdata=testing)
table(pred_rf,testing$classe)
```


###Boosting with trees
```{r, echo=TRUE,eval=FALSE}
modfit_gbm <- train(classe~., method="gbm", data=training, trControl=ctrl2)
pred_gbm <- predict(modfit_gbm,newdata=testing)
table(pred_gbm,testing$classe)
```


All of the three seem to have the same succesfull prediction as shown for classification with trees